\begin{enumerate}[label=\thesection.\arabic*, ref=\thesection.\theenumi]
\item Determine whether the triangle whose lengths of sides are $3 cm, 4 cm, 5 cm$ is a right-angled triangle.
\item $\triangle ABC$ is right-angled at $C$. If $AC = 5 cm$ and $BC = 12 cm$ find the length of $AB$.
\item $PQR$ is a triangle, right-angled at $P$. If $PQ = 10cm$ and $PR = 24 cm$, find $QR$.
\item $ABC$ is a triangle, right-angled at $C$. If $AB = 25 cm$ and $AC = 7 cm$, find $BC$.
\item A $15 m$ long ladder reached a window $12 m$ high from the ground on placing it against a wall at a distance $a$. Find the distance of the foot of the ladder from the wall.
\item  Which of the following can be the sides of a right triangle? 
\begin{enumerate}
	\item $2.5 cm,6.5 cm, 6 cm.$ 
	\item $ 2 cm, 2 cm, 5 cm.$ 
	\item $ 1.5 cm, 2cm, 2.5 cm.$
\end{enumerate}
\item A tree is broken at a height of $5 m$ from the ground and its top touches the ground at a distance of $12 m$ from the base of the tree. Find the original height of the tree.
\item Find the perimeter of the rectangle whose length is $40 cm$ and a diagonal is $41 cm$. 
\item The diagonals of a rhombus measure $16 cm$ and $30 cm$. Find its perimeter.
\item Find the values of the following expressions for $x = 2$. 
	\begin{enumerate}
\item $x + 4$
\item  $4x – 3$ 
\item  $19-5x^2$
\item  $100 – 10x^3$
	\end{enumerate}
\item Find the value of the following expressions when $n = – 2.$ 
	\begin{enumerate}
\item $5n – 2$
\item  $5n^2 + 5n – 2 $
\item  $n^3 + 5n^2 + 5n – 2$
	\end{enumerate}
\item Find the value of the following expressions for $a = 3, b = 2$. 
	\begin{enumerate}
\item $a + b$				
\item $ 7a – 4b $
\item $ a^2+2ab+b^2$
\item $ a^3 – b^3$
\end{enumerate}
\item If $m = 2$, find the value of
	\begin{enumerate}
\item $ m – 2$
\item $ 3m – 5 $
\item $ 9 – 5m $
\item $ 3m^2 – 2m – 7 $
\item $ \frac{5m^4}{ 2}$
\end{enumerate}
\item  If $p = – 2$, find the value of: 
	\begin{enumerate}
\item $4p + 7$
\item  $– 3p^2 + 4p + 7 $
\item  $– 2p^3 – 3p^2 + 4p + 7$
\end{enumerate}
\item  Find the value of the following expressions, when $x = –1$ 
	\begin{enumerate}
\item $ 2x – 7$
\item $ – x + 2$ 
\item $ 2x^2 – x – 2$
\item $ x^2 + 2x +1$
\end{enumerate}
\item  If $a = 2, b = – 2$, find the value of
	\begin{enumerate}
\item  $ a^2 + b^2$
\item  $a^2 + ab + b^2 $
\item  $a^2 – b^2$
\end{enumerate}
\item  When $a = 0, b = – 1$, find the value of the given expressions
	\begin{enumerate}
\item $2a + 2b$
\item $2a^2 + b^2 + 1 $
\item $2a^2b + 2ab^2 + ab $
\item $a^2 + ab + 2$
\end{enumerate}
\item  Simplify the expressions and find the value if $x$ is equal to 2 
	\begin{enumerate}
\item $ x + 7 + 4 (x – 5)$
\item $ 3 (x + 2) + 5x – 7 $
\item $ 6x + 5 (x – 2) $
\item $ 4(2x – 1) + 3x + 11$
\end{enumerate}
\item  Simplify these expressions and find their values if $x = 3, a = – 1, b = – 2$. 
	\begin{enumerate}
\item $ 2x +4 $
\item $6 - 4x$
\item $6 – 5a $
\item $6 – 8b $
\item $3a – 2b-9 $
\end{enumerate}
\item If $z = 10$, find the value of $z^3 – 3(z – 10)$. 
\item  If $p = – 10$, find the value of $p^2 – 2p – 100$
\item  Simplify the expression and find its value when $a = 5$ and $b = – 3$
	$$ 2a^2 + ab + 3 $$
\item What is the circumference of a circle of diameter 10 cm?
\item What is the circumference of a circular disc of radius 14 cm?
\item The radius of a circular pipe is 10 cm. What length of a tape is required to wrap once around the pipe?
\item Sudhanshu divides a circular disc of radius 7 cm in two equal parts. What is the perimeter of each semicircular shape disc?
\item Find the area of a circle of radius 30 cm?
\item Diameter of a circular garden is 9.8 m. Find its area.
\item Find the circumference of the circles with the following radius  
	\begin{enumerate}
		\item 28 mm
\item  14 cm
\end{enumerate}
\item  Find the area of the following circles, given that the radius is
	\begin{enumerate}
\item 14 mm 
\item 5 cm
\item 21 cm 
\item  diameter = 49 m
\end{enumerate}
\item If the circumference of a circular sheet is 154 m, find its radius. Also find the area of the sheet. 
\item A gardener wants to fence a circular garden of diameter 21m. Find the length of the rope he needs to purchase, if he makes 2 rounds of fence. Also find the cost of the rope, if it costs \rupee 4 per meter. 
\item  From a circular sheet of radius 4 cm, a circle of radius 3 cm is removed. Find the area of the remaining sheet. 
\item Seema wants to put a lace on the edge of a circular table cover of diameter 1.5 m. Find the length of the lace required and also find its cost if one meter of the lace costs
\rupee 15. 
\item Find the cost of polishing a circular table-top of diameter 1.6 m, if the rate of polishing is \rupee $15/m^2$. 
\item Shalya took a wire of length 44 cm and bent it into the shape of a circle. Find the radius of that circle. Also find its area. If the same wire is bent into the shape of a square, what will be the length of each of its sides? Which figure encloses more
area, the circle or the square? 
\item From a circular card sheet of radius 14 cm, two circles of radius 3.5 cm and a rectangle of length 3 cm and breadth 1cm are removed. 
 Find the area of the remaining sheet. 
\item A circle of radius 2 cm is cut out from a square piece of an aluminium sheet of side 6 cm. What is the area of the left over aluminium sheet? 
\item  The circumference of a circle is 31.4 cm. Find the radius and the area of the circle. 
\item A circular flower bed is surrounded by a path 4 m wide. The diameter of the flower bed is 66 m. What is the area of this path? 
\item A circular flower garden has an area of $314 m^2$. A sprinkler at the centre of the garden can cover an area that has a radius of 12 m. Will the sprinkler water the entire garden? 
\item Find the circumference of the inner and the outer circles, shown in the adjoining figure? 
\item How many times a wheel of radius 28 cm must rotate to go 352 m? 
\item The minute hand of a circular clock is 15 cm.
	How far does the tip of the minute hand move in 1 hour? 
\item The two sides of the parallelogram ABCD are 6 cm and 4 cm. The height corresponding to the base CD is 3 cm. Find the
	\begin{enumerate}
\item 	area of the parallelogram. 
\item the height corresponding to the base AD.
\end{enumerate}
\item 		\end{enumerate}
